SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-23 docs/questioning.tex
more on section 2

\subsection{Executable Source Code Injection}

@@

In this section we provide a step-by-step exploitation
model

>>>>

\subsection{Executable Source Code Injection Vulnerabilities}

@@

In this section we provide a step-by-step exploitation
model to understand the process of carrying out
application attacks based on executable source code injection
vulnerabilities. Figure~\ref{fig:attacks} presents the steps
of different application attacks. For the most part,
the steps are common for each attack. This is because
they are based on similar attack vectors as we described in
the previous section. We base the analysis of the
existing defenses on this model. Figure~\ref{fig:attacks} also
illustrates in which step the defenses detect corresponding
attacks ({\sc todo}).

An attack starts with the malicious user sending an
request either to the server or to a web user.
In the first case the attacker
could upload data containing a specially crafted script
(in a blog comment) or create a request with
additional {\sc sql} code.
